Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-21 tex/v3/main.tex
change intro
update conclusion

%% formatting appendices
\usepackage{etoolbox}
\patchcmd{\appendices}{\quad}{. }{}{}

@@

%% algorithms
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}

@@

@@

\author{%
Mokhtar Z. Alaya \\
LITIS EA4108\\
University of Rouen\\
\texttt{mokhtarzahdi.alaya@gmail.com} 
\And
Maxime Bérar\\
LITIS EA4108\\
University of Rouen\\
\texttt{maxime.berar@univ-rouen.fr} \\
\And
Gilles Gasso \\
LITIS EA4108\\
INSA, University of Rouen\\
\texttt{gilles.gasso@insa-rouen.fr} 
\And
Alain Rakotomamonjy\\
LITIS EA4108 \\
University of Rouen\\
and Criteo AI Labs, Criteo Paris \\
\texttt{alain.rakoto@insa-rouen.fr} \\
}

@@

\section{Conclusion}
The paper proposed a novel efficient approximation of the Sinkhorn divergence
based on a screening strategy. Screening some of the Sinkhorn dual variables
has been made possible by defining a novel constrained dual problem and by 
carefully analyzing its optimality conditions. From the latter, we derived some
sufficient conditions depending on the ground cost matrix, that some dual variables are smaller than a given threshold. Hence, we need just to solve a restricted
dual Sinkhorn problem using an off-the-shelf LBFGS algorithm. We also provided
some theoretical guarantees of the quality of the approximation with respect to
the number of variables that has been screened. Numerical experiments show 
the behaviour of our \emph{Screenkhorn} algorithm and computational time gain it can
achieve when integrated in some complex machine learning pipelines.

@@

\small
\bibliography{biblio}
\bibliographystyle{plain}

>>>>

%% formatting appendices
\usepackage{etoolbox}
\usepackage{natbib}
\patchcmd{\appendices}{\quad}{. }{}{}

@@

%% algorithms
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{enumitem}

\setlist[itemize]{leftmargin=4.5mm}

@@

\newcommand{\rev}[1]{{\color{blue} #1}}
\newcommand{\ar}[1]{{\color{red} #1}}
\newcommand{\rf}[1]{{\color{green} #1}}

@@

\author{%
Mokhtar Z. Alaya \\
LITIS EA4108\\
University of Rouen\\
\texttt{mokhtarzahdi.alaya@gmail.com} 
\And
Maxime Bérar\\
LITIS EA4108\\
University of Rouen\\
\texttt{maxime.berar@univ-rouen.fr} \\
\And
Gilles Gasso \\
LITIS EA4108\\
INSA, University of Rouen\\
\texttt{gilles.gasso@insa-rouen.fr} 
\And
Alain Rakotomamonjy\\
LITIS EA4108 \\
University of Rouen\\
and Criteo AI Lab, Criteo Paris \\
\texttt{alain.rakoto@insa-rouen.fr} \\
}

@@

\section{Conclusion}
The paper introduces a novel efficient approximation of the Sinkhorn divergence
based on a screening strategy. Screening some of the Sinkhorn dual variables
has been made possible by defining a novel constrained dual problem and by 
carefully analyzing its optimality conditions. From the latter, we derived some
sufficient conditions depending on the ground cost matrix, that some dual variables are smaller than a given threshold. Hence, we need just to solve a restricted
dual Sinkhorn problem using an off-the-shelf LBFGS algorithm. We also provided
some theoretical guarantees of the quality of the approximation with respect to
the number of variables that has been screened. Numerical experiments show 
the behaviour of our \emph{Screenkhorn} algorithm and computational time gain it can
achieve when integrated in some complex machine learning pipelines.

@@

\small
\bibliography{biblio}
\bibliographystyle{chicago}
%well as with those for harvard, apalike, chicago, astron, authordate, and of course natbib.
